### 2020-07-17 latex/sections/introduction.tex
latex work

DL in conjunction with a randomized State-space Search Algorithm Monte-Carlo Tree Search, 
was used to defeat the standing world champion NAME in the incredibly expansive game of Go. This was done in the year 
2017, the researchers used reinforcement learning (RL), where the agent purely played against itself. 
These result imply that given enough time to learn the computer agent is able to
gain a deep insight on how the game should be played.

@@

The method of examining HLC's within games has generally been done by examining the
current state of the game by evaluating them with respect to a heuristic. A heuristic within
games are an evaluation of the end cost for a state given just the state, for example,
the amount of pieces left within a game of chess. Intuitively, the amount of pieces
left is a good estimate for a state in chess, this is a higher level concept we
use to evaluate a chess position. The piece amount can be considered as a lower-level concept
than other concepts we use. For instance, grand master chess players evaluate a position w.r.t. states
where the king is safe from attack, or the structure of the pawn positions.
The idea is to examine a neural networks evaluation of a state regarding
those higher-level concepts, if human players evaluate the king safety of a state
low but the neural network highly values it, and the neural network plays better
than the player. There could be an avenue for us to improve our game by considering king safety more thoroughly.

@@

% The chess engine DeepBlue was the first chess engine to win a chess match agains a
% chess grand master. It's power in the world of chess was a marvel. DeepBlue used tree-
% search to evaluate it's position and possible moves, doing an immense amount of calcluations
% in order to arrive at the best move it could given the time constraints. The tree search
% approach is dependent on knowing which board state is good and what board state is bad,
% This can be easy when the boardstate is such that you're guaranteed to have been checkmated
% in one move, and it's incredibly hard when you boardstate is such that both you and your
% opponent have 16 pieces and are only a handfull of moves in. Generally the boardstate
% is a function of the pieces you have, how safe they are, and how opportunistic you are to
% capture your opponents pieces. These values are not obvious and require a domain expert
% to describe the situations and give the values for these cases.

% The process of evaluating chess positions did not change for many years. With the revival
% of deep neural networks this changed. A neural network is a network of connected nodes (neurons)
% that each how a specific weight. These networks are fed input which is passed through the
% network and it is updated by the weights of the neurons, the input is morphed into
% a more comprehensible value and these values are then used to generate some output.
% The output can be a binary classification for instance input=Image output=\{cat, dog\}.
% Processing the pixels and altering them to numerical values to find the output cat or dog
% is not intuitive and understanding of the values of the neurons in the network
% is not considered fruitful.

% This approach of
% chess engines is still popular today but not the reigning champion anymore. In todays
% best chess engines deep neural networks are used to

% Deep neural network machine learning models have an amazing impact on modern society today,
% we use them to know which items to purchase, to know which people we should love, and we
% use them to drive us to work. These tasks given to deep learning models are all niceties
% for us to enjoy. However, as our dependance on them increases and their astounding success
% in any and all tasks continues, we will want to utilize them for all things. This leads
% to a utopia where decision making is removed from the hands of humans. The question we
% must ask ourselves is when do we want to know why a decision was taken, is it only when
% the decision taken is not preferrable to us. For instance, if a deep neural network model
% used by your lending authority decides you are not worty of a loan. These questions should
% have answers but as it stands today no such answer is possible.

% We can use methods like saliency maps to map a deep learning model emphasis on pixels to
% hopefully understand what portions the model is focusing on. This method however, tells us
% nothing about what

% results that are nothing but amazing.

>>>>

DL in conjunction with a randomized State-space Search Algorithm Monte-Carlo Tree Search, 
was used to defeat the standing world champion Lee Sedol in the incredibly expansive game of Go. This was done in the year 
2017, the researchers used reinforcement learning (RL), where the agent learned by only playing against itself. 
These result imply that given enough time to learn the computer agent is able to
gain a deep insight on how the game should be played.

@@

The method of examining HLC's within games has generally been done by examining the
current state of the game by evaluating them with respect to some heuristic. A heuristic within
games are evaluations of the end reward for a state given only the state, for example,
the amount of pieces left within a game of chess. Intuitively, the amount of pieces
left is a good estimate for a state in chess, this is a higher level concept we
use to evaluate a chess position. The piece amount can be considered as a lower-level concept
than other concepts we use. For instance, grand master chess players evaluate a position w.r.t. states
where the king is safe from attack, or the structure of the pawn positions.
This paper examines a neural networks evaluation of a state regarding
those higher-level concepts, if human players evaluate the king safety of a state
low but the neural network highly values it, and the neural network plays better
than the player. There could be an avenue for us to improve our game by considering king safety more thoroughly.

@@

### 2020-07-17 latex/sections/methods.tex
latex work

\subsection{Policy head}

The policy head of the neural network returns a vector of the size of the action space $w * h * 6$ where $w$ is the width of the board $h$ is the height of the board and $6$ represents the six cardinal direction pawns can move in the space (diagonally both directions, forward and backwards). The vector is then masked s.t. the values representing moves that can not be played on the board are given the value of $0$.

@@

\subsection{Loss Function}

The data collected is backpropagated through the NN moving the weights to the direction of this 
loss function $l = (p * \pi) + (\tau - v)^2$ for each state the NN encountered during self-play.

>>>>

@@

\subsection{Loss Function}
The data collected is backpropagated through the NN moving the weights to the direction of this 
loss function $l = (p * \pi) + (\tau - v)^2$ for each state the NN encountered during self-play.
